Deciding to Disclose: Pregnancy and Alcohol Misuse

### 2014-07-09 Methods.tex
Trying to clear up the notation

\begin{table}
\center
\begin{tabular} {|l | c | r|}
\hline
Name & Description & Value \\ \hline
\(N_{w}\) & Number of women & 1000 \\ \hline
\(N_{m}\) & Number of midwives & 100 \\ \hline
\(A_{m}\) & Number of appointments per midwive & 1000 \\ \hline
\(A_{w}\) & Maximum number of appointments per woman & 12 \\ \hline
R & Runs & 1000 \\ \hline
\(P_{h,w}\) & Proportion of heavy drinkers & \(1/3\) \\ \hline
\(P_{m,w}\) & Proportion of moderate drinkers & \(1/3\) \\ \hline
\(P_{l,w}\) & Proportion of light drinkers & \(1/3\) \\ \hline
\(P_{h,m}\) & Proportion of harsh midwives & \(5/100\) \\ \hline
\(P_{m,m}\) & Proportion of moderate midwives & \(10/100\) \\ \hline
\(P_{l,m}\) & Proportion of non-judgemental midwives & \(85/100\) \\ \hline
\(p_{w}\) & Probability of women sharing & 0. \\ \hline
\(q_{w}\) & Weight of shared information for women & 0. \\ \hline
\(p_{m}\) & Probability of midwives sharing & 0. \\ \hline
\(q_{m}\) & Weight of shared information for midwives & 0. \\ \hline
\(s_{i}[a_{i}]\) & Psuedo-count favouring honesty & 10 \\ \hline
\end{tabular}
\caption[Table caption text]{Model parameters. \label{tab:qt_params}}
\end{table}
\subsection{Global Sensitivity Analysis}
\label{sub:sensitivity}
%Maxmin latin hypercube -> remember to cite the r package used.
%Will require some discussion of the gemsa technique at this point - can also cite Jason H for precedent!
 \cite{Bijak2013b}

@@

\begin{table}
\center
\begin{tabular} {|l | l | l| l|}
\hline
Name & Description & Min & Max \\ \hline
\(P_{h,w}\) & Proportion of heavy drinkers & 0 & 1 \\ \hline
\(P_{m,w}\) & Proportion of moderate drinkers & 0 & 1 \\ \hline
\(P_{l,w}\) & Proportion of light drinkers & 0 & 1 \\ \hline
\(P_{h,m}\) & Proportion of harsh midwives & 0 & 1 \\ \hline
\(P_{m,m}\) & Proportion of moderate midwives & 0 & 1 \\ \hline
\(P_{l,m}\) & Proportion of non-judgemental midwives & 0 & 1 \\ \hline
\(p_{w}\) & Probability of women sharing & 0 & 1 \\ \hline
\(q_{w}\) & Weight of shared information for women & 0 & 1 \\ \hline
\(p_{m}\) & Probability of midwives sharing & 0 & 1 \\ \hline
\(q_{m}\) & Weight of shared information for midwives & 0 & 1 \\ \hline
\(Payoff_{baby}\) & Health payoff for healthy delivery & 1 & 100 \\ \hline
\(Payoff_{referral}\) & Cost for referral & \multicolumn{2}{l|}{\(-(Payoff_{baby} - 1)\)} \\ \hline
\(s_{i}[a_{i}]\) & Psuedo-count favouring honesty & 1 & 100 \\ \hline
\end{tabular}
\caption[Table caption text]{Parameter ranges. \label{tab:sa_params}}
\end{table}

>>>>

\begin{table}
\center
\begin{tabular} {|l | l | c|}
\hline
Name & Description & Value \\ \hline
\(N_{w}\) & Number of women & 1000 \\ \hline
\(N_{m}\) & Number of midwives & 100 \\ \hline
\(R_{m}\) & Number of appointments per midwive & 1000 \\ \hline
\(R_{w}\) & Maximum number of appointments per woman & 12 \\ \hline
Runs & Simulation runs & 1000 \\ \hline
\(P_{h,w}\) & Proportion of heavy drinkers & \(1/3\) \\ \hline
\(P_{m,w}\) & Proportion of moderate drinkers & \(1/3\) \\ \hline
\(P_{l,w}\) & Proportion of light drinkers & \(1/3\) \\ \hline
\(P_{h,m}\) & Proportion of harsh midwives & \(5/100\) \\ \hline
\(P_{m,m}\) & Proportion of moderate midwives & \(10/100\) \\ \hline
\(P_{l,m}\) & Proportion of non-judgemental midwives & \(85/100\) \\ \hline
\(p_{w}\) & Probability of women sharing & 0. \\ \hline
\(q_{w}\) & Weight of shared information for women & 0. \\ \hline
\(p_{m}\) & Probability of midwives sharing & 0. \\ \hline
\(q_{m}\) & Weight of shared information for midwives & 0. \\ \hline
\(s_{i}[a_{i}]:s_{i}[a_{\neg i}]\) & Psuedo-count favouring honesty & 10:1 \\ \hline
\end{tabular}
\caption[Table caption text]{Model parameters. \label{tab:qt_params}}
\end{table}
\subsection{Global Sensitivity Analysis}
\label{sub:sensitivity}
%Maxmin latin hypercube -> remember to cite the r package used.
%Will require some discussion of the gemsa technique at this point - can also cite Jason H for precedent!
In general, we follow the procedure outlined in \cite{Bijak2013b} for stochastic

@@

\begin{table}
\center
\begin{tabular} {|l | l | l| l|}
\hline
Name & Description & Min & Max \\ \hline
\(P_{h,w}\) & Proportion of heavy drinkers & 0 & 1 \\ \hline
\(P_{m,w}\) & Proportion of moderate drinkers & 0 & 1 \\ \hline
\(P_{l,w}\) & Proportion of light drinkers & 0 & 1 \\ \hline
\(P_{h,m}\) & Proportion of harsh midwives & 0 & 1 \\ \hline
\(P_{m,m}\) & Proportion of moderate midwives & 0 & 1 \\ \hline
\(P_{l,m}\) & Proportion of non-judgemental midwives & 0 & 1 \\ \hline
\(p_{w}\) & Probability of women sharing & 0 & 1 \\ \hline
\(q_{w}\) & Weight of shared information for women & 0 & 1 \\ \hline
\(p_{m}\) & Probability of midwives sharing & 0 & 1 \\ \hline
\(q_{m}\) & Weight of shared information for midwives & 0 & 1 \\ \hline
\(P_{h,}\) & Health payoff for healthy delivery & 1 & 100 \\ \hline
\(P_{c, r}\) & Cost for referral & \multicolumn{2}{l|}{\(-(Payoff_{baby} - 1)\)} \\ \hline
\(s_{i}[a_{i}]:s_{i}[a_{\neg i}]\) & Psuedo-count favouring honesty & 1:1 & 100:1 \\ \hline
\end{tabular}
\caption[Table caption text]{Parameter ranges. \label{tab:sa_params}}
\end{table}

### 2014-07-09 Model.tex
Trying to clear up the notation

At the end of a game, each player receives a payoff dependent on the actions and types of both players, which has a partially common interest component. Women receive a payoff based on the health of their eventual baby, with a social cost dependent on the signal they sent and the midwife's reaction to it. Midwives receive the same health payoff as the women, but pay a cost for referring to a specialist, mirroring the organisational cost of non-routine care (table \ref{tab:Payoff-matrix}).

@@

Midwives play for \(A_{m}\) rounds (\(A_{m}=1000\) in all experiments), and conduct appointments in parallel, i.e. if there are 5 midwives, then five women are drawn from the queue and assigned at random to the midwives. 
Unlike women, midwives are only informed of their payoff if they choose to make a referral. Both groups of agents have perfect recall, and midwives are assumed to retrospectively update their observations if they make a referral after a number of appointments.

@@

Formally we let \(S\) be the set of signals \(\{l, m, h\}\), \(T_{w}\) be the set of drinking types \(\{l, m, h\}\), \(T_{m}\) the set of midwife types \(\{l, m, h\}\), and \(J=\{r,n\}\) the actions available to midwives. The set of all payoffs shall be denoted \(P\), where \(P_{w}\) are the payoffs for all women\footnote{While it is assumed that \(P_{w}\) for an individual of type \(a\) is constrained such that \(T=\{a\}\), this can change under the modified game described in subsection \ref{sub:info_sharing}} defined by \(P_{w}=\{x | x=P_{h, b, c} + P_{s, a, d}\wedge b \in J\wedge c \in T\wedge d \in M\}\), and equivalently for midwives \(P_{m}=\{x | x=P_{h, b, c} + P_{c, b}\}\).

@@

The lexicographic heuristic (algorithm \ref{alg:lexico}) follows the form of that used in \cite{Hau2008}, and assumes a simplified decision problem, as in figure \ref{fig:payoff_problem}, where an action is a choice between combined lotteries. Functionally, the heuristic maintains a count of the number of times that each action was followed by a payoff, and chooses the action which most commonly has the best payoff, i.e. one reason decision making. This approach requires minimal computation, and does not assume that all payoffs are known, or static.

Women maintain a count, \(n\) for each of the \(k\) payoffs in \(P_{w, a},a\in k\), an individual payoff paired with a signal, such that \(n_{i}=\{n_{i,1}\ldots n_{i,k}\}\).

Midwives solve a slightly different problem, where the signal received may convey useful information. This is resolved by maintaining a separate count for each signal, i.e. \(n_{i,j}=\{n_{i,j,1}\ldots n_{i, j, k}\}\), and otherwise follow the same algorithm.

@@

The second Bayesian agent augments the payoff reasoning version by separating the two lotteries and assuming that \(P\) is a static, and known set of payoffs possible for the agent. For women, this means that they maintain two sets of beliefs: a Dirichlet mixture which represents the believed distribution of midwife types, and a second set linking signals to referrals.

@@

Midwives reasoning centers determing the meaning of signals, since given the knowledge of what some signal \(i\) conveys about the true type of the sender, the payoff for an action is known. As such, their inference process is the same as for the simple Bayesian agent but over signal-type pairs, and they attempt to minimise -

>>>>

At the end of a game, each player receives a payoff dependent on the actions and types of both players, which has a partially common interest component. Women receive a payoff based on the health of their eventual baby, with a social cost dependent on the signal they sent and the midwife's reaction to it. Midwives receive the same health payoff as the women, but pay a cost for referring to a specialist, mirroring the organisational cost of non-routine care. Table \ref{tab:Payoff-matrix} shows the three payoff matrices which together describe the game.

@@

Midwives play for \(R_{m}\) rounds (\(R_{m}=1000\) in all experiments), and conduct appointments in parallel, i.e. if there are 5 midwives, then five women are drawn from the queue and assigned at random to the midwives. 
Unlike women, midwives are only informed of their payoff if they choose to make a referral. Both groups of agents have perfect recall, and midwives are assumed to retrospectively update their observations if they make a referral after a number of appointments.

Formally then, let \(N = \{m, w\}\) be the set of players each with a private type \(\theta_{i} \in \Theta\), and a set of types \(\Theta=\{l, m, h\}\), with pure strategies \(A_{m}=\{r,n\}, A_{w}=\{l, m, h\}\). Additionally define a utility function \(u_{i}(s_{w}, s_{m}, \theta_{w}, \theta_{m})=P_{s, s_{w}, \theta_{m}} + P_{h, \theta_{w}, s_{m}} + P_{c, \theta_{w}, s_{m}}\), and distributions over types \(p_{w}(l, m, h), p_{m}(l, m, h)\).

@@

@@

The lexicographic heuristic (algorithm \ref{alg:lexico}) follows the form of that used in \cite{Hau2008}, and assumes a simplified decision problem, as in figure \ref{fig:payoff_problem}, where an action is a choice between combined lotteries. Functionally, the heuristic maintains a count of the number of times that each action was followed by a payoff, and chooses the action which most commonly has the best payoff, i.e. one reason decision making. This approach requires minimal computation, and does not assume that \(u_{i}\) is static, or known.

Women resolve this by approximating the utility function, as a function \(f(s_{w}, \sigma)\) on their choice of signal and an unknown distribution, which maps to \(u_{w}\) - i.e. \(s_{w}\) is a choice between simple lotteries. The algorithm maintains a count, \(n\), of the number of occurrences of each outcome given the choice from \(s_{w}\).

Midwives solve a slightly different problem with more information, where \(s_{w}\) is known, and \(s_{m}\) is the lottery choice - \(f(s_{w}, s_{m},\sigma)\). This is resolved by maintaining a separate count for each signal (i.e. \(n_{s_{w},s_{m}}\)), and otherwise following the same algorithm.

@@

The second Bayesian agent augments the reasoning of the simple payoff model, approximating \(u_{w}\) with a more complex function - \(f(s_{w}, \theta_{w}, \sigma_{s}, \sigma_{r})=g(s_{w}, \theta_{w}, \sigma_{s}) + h(s_{w}, \theta_{w}, \sigma_{r})\). For women, this means that they maintain two sets of beliefs: a Dirichlet mixture which represents the believed distribution of midwife types, and a second set linking signals to referrals.

@@

Midwives reasoning centers on determining the meaning of signals, since given the knowledge of what some signal \(i\) conveys about the true type of the sender, the payoff for an action is known. As such, their inference process is the same as for the simple Bayesian agent but over signal-type pairs, and they attempt to minimise -
